preprocessing

### 2022-10-24 r-prep/prep.Rmd
na omit

data_kaya = data_base %>% 
  group_by(ISO,country,year,GDP_pc) %>% 
  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
  left_join(data_iea,data_iea,by=c("ISO","year")) %>%
  mutate(energy_intensity = energy/GDP_pc) %>%
  mutate(carbon_intensity = CO2/energy)

>>>>

data_kaya = data_base %>% 
  group_by(ISO,country,year,GDP_pc) %>% 
  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
  left_join(data_iea,data_iea,by=c("ISO","year")) %>%
  mutate(energy_intensity = energy/GDP_pc) %>%
  mutate(carbon_intensity = CO2/energy) %>%
  na.omit()
